NumPy---Array Programming in Python

### 2020-02-08 body.tex
Move figure
Improve caption

% FIXME SJW: Redraw the icons in vector format
\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{static/sketches/ecosystem}
  \caption{\textbf{Scientific Python Ecosystem.}
   This figure highlights some of the essential tools and libraries, which depend
   on NumPy.  Since most of the ecosystem
   builds on NumPy arrays and its rich and powerful collection of array-aware
   functionality, the simplest way for other array implementations to become
   available to the vast scientific Python ecosystem is by using the NumPy API and array
   protocols (Fig.~\ref{fig:array-protocol}).
  }
  \label{fig:ecosystem}
\end{figure}

>>>>

% FIXME SJW: Redraw the icons in vector format
\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{static/sketches/ecosystem}
  \caption{\textbf{Scientific Python Ecosystem.}
   This figure highlights (in blue) some of the essential tools and libraries that depend
   on NumPy.  Since most of the ecosystem
   builds on NumPy arrays and its rich and powerful collection of array-aware
   functionality, the simplest way for new array implementations to become
   available to the vast scientific Python ecosystem is by using the NumPy API and array
   protocols (Fig.~\ref{fig:array-protocol}).
  }
  \label{fig:ecosystem}
\end{figure}
